POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2024-04-16 challenges/scope-extrusion.tex
Fix a spelling mistake.

\subsubsection{Challenge.}
As in the linearity challence,  we first consider 
 the smalleset relation closed under the six axioms of
 structural congruence, denoted by $\sconga\cdot\cdot$:
\begin{lemma}\label{se-lemma-harmony-facta}
  If \( \sconga{P}{Q} \) and \( \transition{P}{\alpha}{P'} \), then for some \( Q' \) we have \( \transition{Q}{\alpha}{Q'} \) and \( \sconga{P'}{Q'} \).
\end{lemma}
\begin{proof}[Sketch]
By case analysis on the first derivation.
\end{proof}
\begin{lemma}\label{se-lemma-harmony-fact}
  If \( \scong{P}{Q} \) and \( \transition{P}{\alpha}{P'} \), then for some \( Q' \) we have \( \transition{Q}{\alpha}{Q'} \) and \( \scong{P'}{Q'} \).
\end{lemma}
\begin{proof}[Sketch]
    By induction on the structure of the derivation of \( \scong{P}{Q} \), with an inner induction on the structure of a process context and an appeal to Lemma~\ref{se-lemma-harmony-facta}.
\end{proof}

>>>>

\subsubsection{Challenge.}
As in the linearity challence,  we first consider 
 the smallest relation closed under the six axioms of
 structural congruence, denoted by $\sconga\cdot\cdot$:
\begin{lemma}\label{se-lemma-harmony-facta}
  If \( \sconga{P}{Q} \) and \( \transition{P}{\alpha}{P'} \), then for some \( Q' \) we have \( \transition{Q}{\alpha}{Q'} \) and \( \sconga{P'}{Q'} \).
\end{lemma}
\begin{proof}[Sketch]
By case analysis on the first derivation.
\end{proof}
\begin{lemma}\label{se-lemma-harmony-fact}
  If \( \scong{P}{Q} \) and \( \transition{P}{\alpha}{P'} \), then for some \( Q' \) we have \( \transition{Q}{\alpha}{Q'} \) and \( \scong{P'}{Q'} \).
\end{lemma}
\begin{proof}[Sketch]
    By induction on the structure of the derivation of \( \scong{P}{Q} \), with an inner induction on the structure of a process context and an appeal to Lemma~\ref{se-lemma-harmony-facta}.
\end{proof}
